\documentclass[parskip=full]{scrartcl}

\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\usepackage{libertinus}

\begin{document}

\textquote[Ken Thompson]
{One of my most productive days was throwing away 1,000 lines of code.}

\textquote[Brian Kernighan]
{Debugging is twice as hard as writing the code in the first place.
Therefore, if you write the code as cleverly as possible, you are,
by definition, not smart enough to debug it.}
	
\textquote[Martin Fowler]
{Any fool can write code that a computer can understand.
Good programmers write code that humans can understand.}
 
\textquote[Edsger Dijkstra]
{If debugging is the process of removing software bugs, then programming
must be the process of putting them in.}

\textquote[Elon Musk]
{Any product that needs a manual to work is broken.}

\textquote[James Gosling]
{An API that isn't comprehensible isn't usable.}

\textquote[Kent Beck]
{When you program you have think about how someone will read your code,
not just how a computer will interpret it.}

\textquote[suckless.org]
{Ingenious ideas are simple. Ingenious software is simple. Simplicity is
the heart of the Unix philosophy. The more code lines you have removed,
the more progress you have made. As the number of lines of code in your
software shrinks, the more skilled you have become and the less your
software sucks.}

\textquote[Leslie Lamport]
{A distributed system is one in which the failure of a computer you didn't
even know existed can render your own computer unusable.}

\end{document}
